On the properties of projectile motion and quadratic air resistance

### 2016-04-11 Paper/intro.tex
Fixed page numbering
Review of paper by John

\publishers{
	\normalfont\normalsize
	\parbox{0.8\linewidth}{
		The equations of motion for normal projectile motion are derived. Some properties of such motion are defined. Numerical approximations and analytical solutions to the effects of one dimensional quadratic air resistance are made and compared to experimental results with small error. Analytical approximations to two dimensional quadratic air resistance are made using a model which separates low, high and split angle trajectories. The equations of motion for these are derived, plotted and compared to numerical solutions to the original differential equation.
	}
}

@@

>>>>

\publishers{
	\normalfont\normalsize
	\parbox{0.8\linewidth}{
		\todo{Du kommer antagligen tycka att jag ger för många komman i mina exempel, men du får ignorera dem :)}
		The equations of motion for normal \todo{Borde det vara normal? Är det tillräckligt tydligt vad det betyder? Alternativ skulle vara basic?} projectile motion are derived. Some properties of such motion are defined. \todo{Merga till en mening? and some of its properties are defined...}
		\todo{är properties defined? Är de inte determined?} Numerical approximations and analytical solutions to the effects \todo{Borde det vara effects? Kan man säga solutions to effects (lösningar av effekter)} of one dimensional quadratic air resistance are made and compared to experimental results with small error. \todo{Tycker inte man kan säga att de comparades med small error. Föreslår typ... compared to experimental results, producing small error }\todo{Tycker dock hela meningen borde vara typ: One dimensional quadratic air resistance is studied and modeled using numerical and analytical methods and compared to experimental results, producing small error (Det kanske inte är bra, men tycker den kanske borde omformuleras lite)} Analytical approximations to two dimensional quadratic air resistance are made using a model which separates low, high and split angle trajectories. The equations of motion for these are derived, plotted and compared to numerical solutions to the original differential equation. \todo{Här introducerar du plötsligt diff. ekvationer. Kanske borde stå i meningen innan "are modeled (eller described) using differential equations"}
	}
}

@@

	\todo{Har du gjort det här manuellt? Hoppas det är något script eller nåt}
